Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-09-14 paper/aaaiFormat.tex
on introduction

\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Lightweight Transfer Learning from Knowledge Base to Text Stream for High Accurate Event Detection}
\maketitle

@@

\section{Introduction}
Many web applications\cite{ge2015bring}\cite{hughes2009twitter}\cite{sakaki2010earthquake} need the real time event detection technique. 
But the accuracy of existing methods are still far from meeting the application requirements. 
The main stream of existing methods focus on monitoring the changes of the recent data\cite{Allan:2000wu}\cite{Petrovic:2010uj}\cite{Wurzer:2015wq}, and some others use the history data by word frequencies\cite{Li2013JointEE}\cite{Nguyen2015EventDA} and dictionary\cite{Twevent2012}. 
A typical example the existing methods cannot handle well is that ``Russia's anti-ISIS operation in Syria". The word Russia, ISIS, and Syria are trivial, while Russia's anti ISIS is nontrivial because US and other Europe countries but not Russia are the countries that anti ISIS  before September 2015. 
%这个例子应该

To handle this challenge, the important factors on the high accuracy event detection are needed: (1) having a good mechanism to organize the history data, and being aware of what happened; (2) having the capability of self-updating, to accumlate the knowledge about what is happening.

@@

But the existing computation on the RDF graph is often time consuming. To overcome this obtacle, we propose the new data structure \textit{normal states}, which not only utilize the structure adequately but also maintain the information about what happened and what's happening more efficiently than RDF.

@@

\section{Experiments}
\subsection{Effects of History States and Recent States}
Firstly, we demonstrate the effectiveness of history states  initialized from knowledge base and recent states learned by transfer learning.

>>>>

\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Lightweight Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection}
\maketitle

@@

\section{Introduction}
Many web applications need the accurate event detection technique on microblog stream, such as public opinion analysis\cite{thelwall2011sentiment}, public security\cite{Li:2012gw}, and disaster response\cite{Yin:2012ht}, etc.
Although event detection has been a research topic for a long while\cite{allan1998topic}, but event detection in microblog stream is still challenging\cite{atefeh2015survey}.
According to \cite{huang2016probabilistic}, the characteristics of microblog is fast changing, high noise and short length.

Different from the not-well-organized microblog stream, knowledge base (e.g. Wikipedia) is constructed elaborately and contains rich information. 
For this reason, knowledge base can be a good supplementary for event detection on microblog stream.
For example, the tweet ``''

But it's non-trivial to perform transfer learning from knowledge base to microblog stream.

Nowadays knowledge base and text stream are two important channels for people to gain information. 
Usually people learn the facts from knowledge base (e.g. Wikipedia), and get informed the bursty events from text stream (e.g. Twitter).

Existing event detection methods meet the challenges caused by characteristics of the not-well-organized text stream.
Firstly, the posts in the text stream particular diverse.
Second, the posts are noisy. 
These problems can be cut down by incorporating knowledge base.

But the transfer learning from knowledge base to text stream for is non-trivial.
RDF is expensive to apply to the text stream directly.
What the most close method Twevent is designed for pos-precessing rather than incorporating them together.

To handle this challenge, we propose a lightweight transfer learning method, specialized for event detection task. 
There are two designed data structure to balance the performance and cost.  
\textit{History states} are. 
\textit{Recent states} are.

\begin{comment}
Many web applications\cite{ge2015bring}\cite{hughes2009twitter}\cite{sakaki2010earthquake} need the real time event detection technique. 
But the accuracy of existing methods are still far from meeting the application requirements. 
The main stream of existing methods focus on monitoring the changes of the recent data\cite{Allan:2000wu}\cite{Petrovic:2010uj}\cite{Wurzer:2015wq}, and some others use the history data by word frequencies\cite{Li2013JointEE}\cite{Nguyen2015EventDA} and dictionary\cite{Twevent2012}. 
A typical example the existing methods cannot handle well is that ``Russia's anti-ISIS operation in Syria". The word Russia, ISIS, and Syria are trivial, while Russia's anti ISIS is nontrivial because US and other Europe countries but not Russia are the countries that anti ISIS  before September 2015. 
%这个例子应该

To handle this challenge, the important factors on the high accuracy event detection are needed: (1) having a good mechanism to organize the history data, and being aware of what happened; (2) having the capability of self-updating, to accumlate the knowledge about what is happening.
\end{comment}

@@

\begin{comment}
But the existing computation on the RDF graph is often time consuming. To overcome this obtacle, we propose the new data structure \textit{normal states}, which not only utilize the structure adequately but also maintain the information about what happened and what's happening more efficiently than RDF.  
\end{comment}

@@

\section{Experiments}
\subsection{Effects of History States and Recent States}
In this subsection, we demonstrate the effectiveness of \textit{history states} initialized from knowledge base and \textit{recent states} learned by transfer learning.
